\section{Proposed work plan}
\subsection{Milestones}
\begin{enumerate}
    \item \textbf{Baseline reproduction (Weeks 1--3):} Implement reference pseudo-spectral and finite-volume solvers with standard projection/CT and divergence-cleaning options. Validate on Taylor--Green vortex and Orszag--Tang vortex tests.
    \item \textbf{Constraint metrics suite (Weeks 2--4):} Build diagnostics for $\|\divergence \uu\|$, $\|\divergence \BB\|$, energy spectra, and helicity/energy drift.
    \item \textbf{ML surrogate design (Weeks 4--8):} Develop two candidates: (a) neural-operator predictor followed by classical projection; (b) divergence-free architecture (vector potential) delivering hard constraints. Train on DNS snapshots with randomized Reynolds numbers and forcings.
    \item \textbf{Accelerated projection/preconditioner (Weeks 6--10):} Train learned multigrid or neural preconditioner for Poisson solves; integrate into baseline.
    \item \textbf{Evaluation and ablations (Weeks 9--12):} Compare runtime, constraint violations, and stability across baselines and ML hybrids. Study generalization to unseen Reynolds numbers and boundary conditions.
    \item \textbf{Documentation and release (Weeks 12--14):} Package code with configuration files, seeds, and experiment scripts. Release trained weights and logs.
\end{enumerate}

\subsection{Implementation sketch}
\begin{itemize}
    \item \textbf{Data pipeline:} Store training data as HDF5 or Zarr tensors; include metadata (Reynolds number, resolution, forcing). Provide scripts for generating synthetic DNS snapshots.
    \item \textbf{Model zoo:} FNO/DeepONet with optional Helmholtz projection layer; divergence-free convolutional networks using vector potentials; learned multigrid components.
    \item \textbf{Integration:} Wrap ML modules as drop-in components inside a time-stepping loop with optional gradient tracking for differentiable experiments.
    \item \textbf{Configuration:} YAML or TOML configs specifying PDE parameters, loss weights for constraints, and solver options. Provide default seeds and deterministic cuDNN settings when applicable.
\end{itemize}
